%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
\label{literatura}
\addcontentsline{toc}{chapter}{Literatúra}

\bibitem{hvlab}
HWANG Wu-Yuin, HAREGOT Michaele, KONGCHAROEN Chaknarin (2017) {\it Web-based hybrid virtualization laboratory to facilitate network learning: HVLab}. IEEE Conference Publication. ISBN: 978-1-5386-1431-0

\bibitem{opennebula_lab}
Yu.A. USHAKOV, P.N. POLEZHAEV, L.V. LEGASHEV, A.E. SHUKHMAN, I.P. BOLODURINA (2016) {\it  Virtual cloud network laboratory based on IaaS with automatized creation of network topology on demand }. IEEE Conference Publication. ISBN: 978-1-5090-1841-3

\bibitem{packet_tracer}
Cisco Systems, Inc. (03-26-2018) {\it Introduction to Packet Tracer | Cisco NetAcad}. [Online] [cit. 2018-03-27]. \\ 
Dostupné na: <\url{https://www.netacad.com/courses/intro-packet-tracer/}>.

\bibitem{packet_tracer_mac}
MCKENZIE Peter (10-17-2016) {\it Where to find packet tracer for Mac OS? How to install it? - 101872 - The Cisco Learning Network}. [Online] [cit. 2018-03-27]. \\
Dostupné na: <\url{https://learningnetwork.cisco.com/thread/101872}>.

\bibitem{obr_packet_tracer}
ccnav6.com (07-05-2017) {\it 7.1.1.4 Packet Tracer - ACL Demonstration Instructions Answers}. [Online] [cit. 2018-03-25]. \\ 
Dostupné na: <\url{https://ccnav6.com/wp-content/uploads/2017/07/7.1.1.4-Packet-Tracer-ACL-Demonstration-Instructions.jpg}>.

\bibitem{dynamips}
EasyPass Computer Training Centre (05-08-2016) {\it Dynamips / Dynagen Tutorial}. [Online] [cit. 2018-03-25]. \\ 
Dostupné na: <\url{http://www.iteasypass.com/Dynamips.htm}>.

\bibitem{obr_dynamips_dynagen}
EasyPass Computer Training Centre (05-08-2016) {\it Dynamips / Dynagen Tutorial}. [Online] [cit. 2018-03-25]. \\ 
Dostupné na: <\url{http://www.iteasypass.com/Dynamips\%20-\%20Dynagen\%20Tutorial.files/image002.gif}>

\bibitem{dynamips_github}
DUPONCHELLE Julien, LINTOTT Daniel, GROSSMANN Jeremy (07-24-2017) {\it GNS3/dynamips: Dynamips development}. [Online] [cit. 2018-03-25]. \\ 
Dostupné na: <\url{https://github.com/GNS3/dynamips}>.

\bibitem{dynamips_nil}
SEGEČ Pavel, NIL - Network Information Library (04-11-2014) {\it Connecting Dynamips/Dynagen router with a real network - in linux | NIL - Network Information Library}. [Online] [cit. 2018-03-25]. \\ 
Dostupné na: <\url{http://nil.uniza.sk/network-simulation-and-modelling/dynamipsdynagen/connecting-dynamipsdynagen-router-real-network-linux}>.

\bibitem{webiou_unetlab_unetlabv2}
Route Reflector Labs (03-21-2018) {\it Unified Networking Lab v2 (UNetLabv2) | Andrea Dainese}. [Online] [cit. 2018-03-25]. \\
Dostupné na: <\url{http://www.routereflector.com/unetlab/}>.

\bibitem{webiou_github}
DAINESE Andrea (05-30-2016) {\it dainok/iou-web}. [Online] [cit. 2018-03-25]. \\
Dostupné na: <\url{https://github.com/dainok/iou-web}>.

\bibitem{webiou_firewall_cx}
WANG Jack (2017) {\it Cisco IOU}. [Online] [cit. 2018-03-25]. \\
Dostupné na: \\
%<\url{http://www.firewall.cx/cisco-technical-knowledgebase/cisco-services-tech/1172-cisco-virl-virtual-internet-routing-lab-introduction.html}>.
\href{http://www.firewall.cx/cisco-technical-knowledgebase/cisco-services-tech/1172-cisco-virl-virtual-internet-routing-lab-introduction.html}{<\texttt{http://www.firewall.cx/cisco-technical-knowledgebase/cisco-services-\\tech/1172-cisco-virl-virtual-internet-routing-lab-introduction.html}>}.

\bibitem{webiou_80211}
FORDHAM Stuart (06-15-2013) {\it Getting started with Cisco IOU - IOS on Unix - Part 1 | www.802101.com}. [Online] [cit. 2018-03-25]. \\
Dostupné na: \\
<\url{https://www.802101.com/getting-started-cisco-iou-ios-unix/}>.

\bibitem{webiou_real_network}
FERRO Greg (04-17-2011) {\it Cisco IOU:Connect IOU with real or external networks — EtherealMind}. [Online] [cit. 2018-03-25]. \\
Dostupné na: \\<\url{http://etherealmind.com/cisco-iou-external-real-network-remote/}>.

\bibitem{obr_webiou}
FARES Ryan (12-10-2015) {\it Cisco IOU Web Interface – netbrainstlearn}. [Online] [cit. 2018-03-25]. \\
Dostupné na: \\
<\url{https://i2.wp.com/www.routereflector.com/images/posts/2012/09/iou-web-new.png}>.

\bibitem{virl_cisco}
Cisco Systems, Inc. (2018) {\it Cisco Virtual Internet Routing Lab Personal Edition (VIRL PE) 20 Nodes - The Cisco Learning Network}. [Online] [cit. 2018-03-26]. \\
Dostupné na: \\
\href{https://learningnetworkstore.cisco.com/virtual-internet-routing-lab-virl/cisco-personal-edition-pe-20-nodes-virl-20}{<\texttt{https://learningnetworkstore.cisco.com/virtual-internet-routing-lab\\-virl/cisco-personal-edition-pe-20-nodes-virl-20}>}.

\bibitem{virl_interfacett_1}
JACOB Mark, Interface Technical Training (08-14-2015) {\it How to create a simple network topology using Cisco VIRL}. [Online] [cit. 2018-03-26]. \\
Dostupné na: \\
\href{https://www.interfacett.com/blogs/how-to-create-a-simple-network-topology-using-ciscos-virl/}{<\texttt{https://www.interfacett.com/blogs/how-to-create-a-simple-network\\-topology-using-ciscos-virl/}>}.

\bibitem{virl_interfacett_2}
JACOB Mark, Interface Technical Training (08-28-2015) {\it How to interact with a simple network topology built using Cisco’s VIRL}. [Online] [cit. 2018-03-26]. \\
Dostupné na: \\
\href{https://www.interfacett.com/blogs/how-to-interact-with-a-simple-network-topology-built-using-ciscos-virl/}{<\texttt{https://www.interfacett.com/blogs/how-to-interact-with-a-simple\\-network-topology-built-using-ciscos-virl/}>}.

\bibitem{virl_ciscoskills}
Cisco Skills (01-07-2017) {\it Cisco VIRL and Windows VMs}. [Online] [cit. 2018-03-26]. \\
Dostupné na: \\<\url{https://ciscoskills.net/2017/01/07/cisco-virl-and-windows-vms/}>.

\bibitem{virl_speaknetworks}
WANG Jack (07-27-2015) {\it Cisco VIRL External Connectivity – Speak Network Solutions}. [Online] [cit. 2018-03-26]. \\
Dostupné na: \\<\url{https://www.speaknetworks.com/cisco-virl-external-connectivity/}>.

\bibitem{virl_cisco_features}
Cisco Systems, Inc. (2018) {\it Virtual Internet Routing Lab (VIRL) Features - The Cisco Learning Network Store}. [Online] [cit. 2018-03-26]. \\
Dostupné na: <\url{https://learningnetworkstore.cisco.com/virlfaq/features}>.

\bibitem{virl_edition_differences}
LIU Wen, Inc. (04-28-2016) {\it VIRL Personal Edition vs. the Academic Edition - 30411 - The Cisco Learning Network}. [Online] [cit. 2018-03-26]. \\
Dostupné na: <\url{https://learningnetwork.cisco.com/docs/DOC-30411}>.

\bibitem{obr_virl_vmmaestro}
JACOB Mark, Interface Technical Training (08-28-2015) {\it How to interact with a simple network topology built using Cisco’s VIRL}. [Online] [cit. 2018-03-26]. \\
Dostupné na: \\
<\url{https://www.interfacett.com/wp-content/uploads/2015/08/013-interact-with-simple-network-topology-in-Cisco-VIRL.jpg}>.

\bibitem{obr_virl_web}
JACOB Mark, Interface Technical Training (08-28-2015) {\it How to interact with a simple network topology built using Cisco’s VIRL}. [Online] [cit. 2018-03-26]. \\
Dostupné na: \\
<\url{https://www.interfacett.com/wp-content/uploads/2015/08/013-interact-with-simple-network-topology-in-Cisco-VIRL.jpg}>.

\bibitem{incapsula_cms}
CASSETTO Orion (09-26-2017) {\it Why CMS Platforms Are Common Hacking Targets | Security Tips}. [Online] [cit. 2018-04-13]. \\
Dostupné na: \\
<\url{https://www.incapsula.com/blog/cms-security-tips.html}>.

\bibitem{viro_hadac}
HADAČ Peter (04-27-2017) {\it ViRo2 - online web nástroj na podporu vyučovania sietí}. [Online] [cit. 2018-03-26] str. 32-36, 52-55. \\
Dostupné na: \\
<\url{http://opac.crzp.sk/?fn=detailBiblioForm&sid=F972C28947B4ECBEDC061D4570AC&seo=CRZP-detail-kniha}>.

\bibitem{stackoverflow_survey}
Stack Exchange Inc (2018-03-19) {\it Stack Overflow Developer Survey 2018}. [Online] [cit. 2018-03-27] \\
Dostupné na: \\
<\url{https://insights.stackoverflow.com/survey/2018/?utm_source=Iterable&utm_medium=email&utm_campaign=dev-survey-2018-promotion#most-loved-dreaded-and-wanted}>.

\bibitem{unetlab_github}
DAINESE Andrea (05-23-2017) {\it dainok/iou-web}. [Online] [cit. 2018-03-26]. \\
Dostupné na: <\url{https://github.com/dainok/iou-web}>.

\bibitem{obr_unetlab_web}
HAGEN, LAN-Monitor.de  (03-19-2016) {\it Was ist UNetLab? – LAN-Monitor.de}. [Online] [cit. 2018-03-26]. \\
Dostupné na: \\
<\url{https://www.lan-monitor.de/wp-content/uploads/was-ist-unetlab-01-test-lab.png}>.

\bibitem{obr_unetlabv2_arch}
DAINESE Andrea, Route Reflector Labs (03-21-2018) {\it Unified Networking Lab v2 (UNetLabv2) | Andrea Dainese}. [Online] [cit. 2018-03-26]. \\
Dostupné na: \\
<\url{http://www.routereflector.com/images/unetlab/unetlab-architecture.png}>.

\bibitem{eve_ng_technologies}
BuiltWith® Pty Ltd (03-26-2018) {\it IP\_adresa\_servera Technology Profile}. [Online] [cit. 2018-03-26]. \\
Dostupné na: <\url{https://builtwith.com/IP\_adresa\_servera}>.

\bibitem{eve_ng_versions_table}
EVE-NG Ltd. (2018) {\it Compare Editions}. [Online] [cit. 2018-03-26]. \\
Dostupné na: <\url{http://www.eve-ng.net/index.php/features/compare}>.

\bibitem{eve_ng_versions_list}
EVE-NG Ltd. (2018) {\it Features}. [Online] [cit. 2018-03-26]. \\
Dostupné na: <\url{http://www.eve-ng.net/index.php/features/features}>.

\bibitem{gns3_docker}
ZIAJKA Dominik, GROSSMANN Jeremy, DUPONCHELLE Julien (02-08-2018) {\it Docker support in GNS3 - GNS3}. [Online] [cit. 2018-03-26]. \\
Dostupné na: \\
<\url{https://docs.gns3.com/1KGkv1Vm5EgeDusk1qS1svacpuQ1ZUQSVK3XqJ01WKGc/}>.

\bibitem{gns3_gui_github}
ZIAJKA Dominik, GROSSMANN Jeremy (03-12-2018) {\it GNS3/gns3-gui: GNS3 Graphical Network Simulator: GNS3 server}. [Online] [cit. 2018-03-27]. \\
Dostupné na: <\url{https://github.com/GNS3/gns3-gui}>.

\bibitem{gns3_server_github}
ZIAJKA Dominik, GROSSMANN Jeremy (03-14-2018) {\it GNS3/gns3-server: GNS3 server}. [Online] [cit. 2018-03-27]. \\
Dostupné na: <\url{https://github.com/GNS3/gns3-server}>.

\bibitem{gns3_web_github}
ZIAJKA Dominik (03-26-2018) {\it GNS3/gns3-web-ui: WebUI implementation for GNS3}. [Online] [cit. 2018-03-27]. \\
Dostupné na: <\url{https://github.com/GNS3/gns3-web-ui}>.

\bibitem{gns3_console_ports}
ZUPPETTA Bruno Paolo (September 2017) {\it Discussions - Console port - GNS3}. [Online] [cit. 2018-03-27]. \\
Dostupné na: <\url{https://www.gns3.com/qa/console-port-2}>.

\bibitem{gns3_console_ports_remote}
LOOKY Silva (06-05-2017) {\it Discussions - Edit the default "Console Port Range" for remote server ? - GNS3}. [Online] [cit. 2018-03-27]. \\
Dostupné na: \\
<\url{https://www.gns3.com/discussions/edit-the-default-console-port-ra}>.

\bibitem{nested_virtualization}
VMware, Inc. (03-11-2016) {\it GNS3/gns3-server: GNS3 server}. [Online] [cit. 2018-03-27]. \\
Dostupné na: <\url{https://communities.vmware.com/docs/DOC-8970}>.

\bibitem{ccna_security_topics}
Cisco Systems, Inc. (02-07-2018) {\it IINS Exam Topics - The Cisco Learning Network}. [Online] [cit. 2018-03-31]. \\
Dostupné na: \\
<\url{https://learningnetwork.cisco.com/community/certifications/security_ccna/iins-v3/exam-topics}>.

\bibitem{eve_ng_howtos}
EVE-NG Ltd. (04-01-2018) {\it HowTo's}. [Online] [cit. 2018-04-01]. \\
Dostupné na: <\url{http://www.eve-ng.net/index.php/documentation/howto-s/}>.

\bibitem{eve_ng_faq}
EVE-NG Ltd. (03-31-2018) {\it FAQ}. [Online] [cit. 2018-04-03]. \\
Dostupné na: <\url{http://www.eve-ng.net/index.php/faq}>.

\bibitem{eve_ng_integration_pack_win}
EVE-NG Ltd. {\it Windows Client side Pack}. [Online] [cit. 2018-04-16]. \\
Dostupné na: \\
<\url{http://www.eve-ng.net/downloads/windows-client-side-pack}>.

\bibitem{eve_ng_integration_pack_linux}
EVE-NG Ltd. {\it Linux Client side Pack}. [Online] [cit. 2018-04-16]. \\
Dostupné na: <\url{http://www.eve-ng.net/downloads/linux-client-side}>.

\end{thebibliography}

